Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-01 popl24/composition.tex
checkpoint

Our results in Section \ref{section-pre-post} and Theorem
\ref{theorem-nimo} imply that any well-typed program using
$\ttt{encode}$, $\ttt{andgg}$, and $\ttt{decode}$ will generate a
circuit that is passive secure, provided that gate outputs are
not used more than once. To add an $\ttt{or}$ gate to our
library, we can use $\ttt{andgg}$ as a template, in fact simple
modification of $\ttt{andtable}$ is all that would be needed. Thus,
this library embodies a Fairplay-like language where well-typedness
of metaprograms guarantees safety and security of generated protocols.

>>>>

Theorem \ref{theorem-nimo} means that any well-typed program using
$\ttt{encode}$, $\ttt{andgg}$, and $\ttt{decode}$ will generate a
circuit that is passive secure, provided that gate outputs are not
used more than once. To add an $\ttt{or}$ gate to our library, we can
use $\ttt{andgg}$ as a template, in fact simple modification of
$\ttt{andtable}$ is all that would be needed. Thus, this library
embodies a Fairplay-like language where well-typedness of metaprograms
guarantees safety and security of generated protocols.
